---
title: "ESM 204 - Assignment 4"
author: "Brad Anderson and Andrew Steinkruger"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

#### Appendix: Formulas and Calculations

```{r setup, include=FALSE}

# Set packages.
library(readr)
library(knitr)
library(here)
library(tidyverse)
library(gapminder)
library(sandwich)
library(broom)
library(lmtest)
library(stargazer)

# Set data.
set_here()
dat <- read_csv('dat.csv')

```

#### 1. Marginal Cost Estimation

$$ MC_i = \beta_{0, i} + \beta_{1, i} * x_{abatement} + u_i$$
Add explicit functions for each sector.

Add explanation.

```{r 1}
# Check scatters.
#qplot(Abatement, MC_A, data = dat)
#qplot(Abatement, MC_B, data = dat)
#qplot(Abatement, MC_C, data = dat)
#qplot(Abatement, MC_D, data = dat)

# Fit linear models.
model_a <- lm(MC_A ~ Abatement, data = dat)
model_b <- lm(MC_B ~ Abatement, data = dat)
model_c <- lm(MC_C ~ Abatement, data = dat)
model_d <- lm(MC_D ~ Abatement, data = dat)

# Save coefficients.
#coef_a <-as.data.frame(t(coefficients(model_a)))
#coef

# Prepare supply data for plotting.
dat_plot_supply <- 
  reshape2::melt(dat, id.vars = "Abatement") %>%
  bind_cols(., 
            bind_rows(data.frame(predict(model_a, interval = "confidence", level = 0.95)),
                      data.frame(predict(model_b, interval = "confidence", level = 0.95)),
                      data.frame(predict(model_c, interval = "confidence", level = 0.95)),
                      data.frame(predict(model_d, interval = "confidence", level = 0.95))))

# Plot supply.
ggplot(dat_plot_supply, 
         aes(Abatement,
             value,
             group = variable,
             color = variable)) +
        geom_point(alpha = .9) +
        geom_line(aes(Abatement, 
                      fit, 
                      group = variable)) +
        geom_ribbon(aes(Abatement, 
                        ymin = lwr, 
                        ymax = upr, 
                        group = variable, 
                        fill = variable), 
                    alpha = 0.05, 
                    color = NA, 
                    show.legend = FALSE) +
        labs(x = "Abatement", 
             y = "Price",
             title = "Estimated Marginal Costs of Abatement by Sector",
             color = "Sector") +
        theme_classic() +
        coord_cartesian(expand = FALSE) +
        scale_colour_hue(h = c(90, 270))

```

#### 2. Demand Estimation

$$ d_i = \alpha_{0, i} - \alpha_{1, i} * x_{emissions} + u_i$$

Add explicit functions for each sector.

Add explanation.

```{r 2}
# Set supply x-maxima.
xmax_a = 180
xmax_b = 200
xmax_c = 220
xmax_d = 300
# Set supply coefficients.
b0_a <- unname(model_a$coefficients[1])
b1_a <- unname(model_a$coefficients[2])
b0_b <- unname(model_b$coefficients[1])
b1_b <- unname(model_b$coefficients[2])
b0_c <- unname(model_c$coefficients[1])
b1_c <- unname(model_c$coefficients[2])
b0_d <- unname(model_d$coefficients[1])
b1_d <- unname(model_d$coefficients[2])
# Set supply functions..
s_a <- function(Abatement){
                           supply_a <- b0_a + b1_a * Abatement 
                           return(supply_a)
                           }
s_b <- function(Abatement){
                           supply_b <- b0_b + b1_b * Abatement 
                           return(supply_b)
                           }
s_c <- function(Abatement){
                           supply_c <- b0_c + b1_c * Abatement 
                           return(supply_c)
                           }
s_d <- function(Abatement){
                           supply_d <- b0_d + b1_d * Abatement 
                           return(supply_d)
                           }
# Set demand y-intercepts.
a0_a <- b1_a * xmax_a
a0_b <- b1_b * xmax_b
a0_c <- b1_c * xmax_c
a0_d <- b1_d * xmax_d

# Set demand slopes.
a1_a <- -b1_a
a1_b <- -b1_b
a1_c <- -b1_c
a1_d <- -b1_d


# Set demand functions.
d_a <- function(Emissions){
                           demand_a <- a0_a + a1_a * Emissions
                           return(demand_a)
                           }
d_b <- function(Emissions){
                           demand_b <- a0_b + a1_b * Emissions
                           return(demand_b)
                           }
d_c <- function(Emissions){
                           demand_c <- a0_c + a1_c * Emissions
                           return(demand_c)
                           }
d_d <- function(Emissions){
                           demand_d <- a0_d + a1_d * Emissions
                           return(demand_d)
                           }
# Plot demand functions.
ggplot(data.frame(Emissions = c(0, 300)),
       aes(Emissions)) +
       stat_function(fun = d_a, geom = "line", xlim = c(0, 180)) +
       stat_function(fun = d_b, geom = "line", xlim = c(0, 200)) +
       stat_function(fun = d_c, geom = "line", xlim = c(0, 220)) +
       stat_function(fun = d_d, geom = "line", xlim = c(0, 300)) +
       labs(x = "Emissions", 
            y = "Price",
            title = "Estimated Marginal Benefits of Emissions by Sector") +
       theme_classic() +
       coord_cartesian(expand = FALSE)

```

#### 3. Costs and Benefits of Emission Reduction Policy Options

**Add analytical solutions from notes once it's all done.**

##### a. Cap

```{r 3a}
# Run cost by sector.
# Check whether stats::integrate() is working right.
tc_a_a <- integrate(d_a, xmax_a-100, xmax_a)
tc_a_b <- integrate(d_b, xmax_b-100, xmax_b) 
tc_a_c <- integrate(d_c, xmax_c-100, xmax_c)
tc_a_agg <- sum(tc_a_a$value, tc_a_b$value, tc_a_c$value)

tc_a_a$value
tc_a_b$value
tc_a_c$value
tc_a_agg
```

##### b. Tax

```{r 3b}
# Find t.
  # Set aggregate supply function.
    # Set inner functions.
d_a_q <- function(Price){
  demand_a <- -(a0_a - Price)/a1_a
  return(demand_a)
}
d_b_q <- function(Price){
  demand_b <- -(a0_b - Price)/a1_b
  return(demand_b)
}
d_c_q <- function(Price){
  demand_c <- -(a0_c - Price)/a1_c
  return(demand_c)
}
d_d_q <- function(Price){
  demand_d <- -(a0_d - Price)/a1_d
  return(demand_d)
} 

d_bac_q <- function(Price){
  demand_bac_q <- -((a0_b - Price)/a1_b + (a0_a - Price)/a1_a + (a0_c - Price)/a1_c)
  return(demand_bac_q)
} 

d_ac_q <- function(Price){
  demand_ac_q <- -((a0_a - Price)/a1_a + (a0_c - Price)/a1_c)
  return(demand_ac_q)
} 

# Get aggregate function from the plot.
ggplot(data.frame(Price = c(0, a0_c)),
       aes(Price)) +
       stat_function(fun = d_bac_q, geom = "line", xlim = c(0, a0_b)) +
       stat_function(fun = d_ac_q, geom = "line", xlim = c(a0_b, a0_a)) +
       stat_function(fun = d_c_q, geom = "line", xlim = c(a0_a, a0_c)) +
       stat_function(fun = d_c_q, geom = "line", xlim = c(0, a0_c)) +
       stat_function(fun = d_a_q, geom = "line", xlim = c(0, a0_a)) +
       stat_function(fun = d_b_q, geom = "line", xlim = c(0, a0_b)) +
       labs(x = "Price", 
            y = "Emissions",
            title = "Estimated Marginal Benefits of Emissions by Sector") +
       theme_classic() +
       coord_flip(expand = FALSE)


# Plot stuff to get the answer.
p <- vector(length = 200)
p <- seq(0, 199)
agg <- vector(length = length(p))
b <- vector(length = length(p))
a <- vector(length = length(p))
c <- vector(length = length(p))
agg[1:a0_b] <- d_bac_q(p)
agg[a0_b:a0_a] <- d_ac_q(p[a0_b:a0_a])
agg[a0_a:a0_c] <- d_c_q(p[a0_a:a0_c])
b[1:200] <- d_b_q(p)
a[1:200] <- d_a_q(p)
c[1:200] <- d_c_q(p)
  
solve <- data.frame(p, agg, c, a, b)

# Find the tax and cap-and-trade equilibrium price by hand-substitution.
t <- 37.309
t

# Set new cost functions incorporating t.
dt_a <- function(Abatement){
  demand_tax_a <- a0_a - t + a1_a * Abatement
  return(demand_tax_a)
}
dt_b <- function(Abatement){
  demand_tax_b <- a0_b - t + a1_a * Abatement
  return(demand_tax_b)
}
dt_c <- function(Abatement){
  demand_tax_c <- a0_c - t + a1_a * Abatement
  return(demand_tax_c)
}

# Integrate for total costs.
tb_b_a <- integrate(d_a, 0, -a0_a/a1_a) 
tbt_b_a <- integrate(dt_a, 0, -(a0_a - t)/a1_a)
tc_b_a <- tbt_b_a$value - tb_b_a$value
tc_b_a

tb_b_b <- integrate(d_b, 0, -a0_b/a1_b) 
tbt_b_b <- integrate(dt_b, 0, -(a0_b - t)/a1_b)
tc_b_b <- tbt_b_b$value - tb_b_b$value
tc_b_b

tb_b_c <- integrate(d_c, 0, -a0_c/a1_c) 
tbt_b_c <- integrate(dt_c, 0, -(a0_c - t)/a1_c)
tc_b_c <- tbt_b_c$value - tb_b_c$value
tc_b_c

tc_b_agg <- tc_b_a + tc_b_b + tc_b_c

# Integrate tax revenue.
trp_b_a <- integrate(d_a, 0, -(a0_a - t)/a1_a)
trm_b_a <- integrate(dt_a, 0, -(a0_a - t)/a1_a)
trp_b_b <- integrate(d_b, 0, -(a0_b - t)/a1_b)
trm_b_b <- integrate(dt_b, 0, -(a0_b - t)/a1_b)
trp_b_c <- integrate(d_c, 0, -(a0_c - t)/a1_c)
trm_b_c <- integrate(dt_c, 0, -(a0_c - t)/a1_c)
tr_b_agg <- sum(trp_b_a$value - trm_b_a$value + trp_b_b$value - trm_b_b$value + trp_b_c$value - trm_b_c$value)
tr_b_agg

```

##### c. Cap and Trade

```{r 3c, eval = FALSE}
# Reuse t from 3b to get quantities for each sector.
d_a_q(t)
d_b_q(t)
d_c_q(t)

# Check that they get to 300.
d_a_q(t) + d_b_q(t) + d_c_q(t)

# Get costs, sum costs, sum benefits.
tc_c_a <- integrate(d_a, d_a_q(t), -a0_a/a1_a)
tc_c_b <- integrate(d_b, d_b_q(t), -a0_b/a1_b)
tc_c_c <- integrate(d_c, d_c_q(t), -a0_c/a1_c)
tc_c_agg <- sum(tc_c_a$value, tc_c_b$value, tc_c_c$value)

tc_c_a$value
tc_c_b$value
tc_c_c$value
tc_c_agg
```

#### 5. Implications of Carbon Market Entry for Air Pollution

##### a. Air Pollution - No Entry

Both countries must emit 300 tons of local air pollution, with the values for tons of emissions given from questions **(1)** - **(5)**.

##### a. Air Pollution - Entry by Country Y

```{r 5b}



```

